Fission product decay chain equilibria in \zirconia

### 2019-03-08 manuscript.tex
Update fission yields

Nuclear fuel claddings have unique materials challenges owing to the highly active environment in which they operate and the creation of unstable isotopes. Corrosive species in the pin such as iodine, produced directly as a result of uranium fission are known to play a role in SCC \cite{Sidky1998, Fregonese1998, iodinezrmetal}. However, iodine nuclei produced from fission are unstable. Fission of uranium produces iodine precursors, mainly unstable isotopes of tellurium. Both iodine and tellurium are relatively common fission products, with combined independent yields from thermal fission of U$_{235}$ of more than 5\% \cite{kennett1956mass, iodine129fissionyield, imanishi1976independent, iaeafissionyield, iodine132, amiel1975odd}. In addition, xenon and caesium are also common fission products, as shown in Figure \ref{fig:fissionyield}, with fission product masses firmly within the heavy nuclide peak of uranium and plutonium fission product distribution curves.    \\

@@

\begin{table}
\caption{Independent fission product yields and half-lives for the major iodine isotopes and precursors in a thermal neutron reactor. Yields from \cite{iodinefissionyields, iodine132}. All isotopes undergo single $\beta$- decay. Metastable states are included.}  \label{table:decaydata}
\begin{center}
\begin{tabular}{c c c}
\hline
Isotope & Independent Yield (\%) & Half-life \\
\hline
\texorpdfstring{I\textsubscript{131}}{I131} & 0.00136 $\pm 0.00047$ & 8.023 d \cite{I131halflife} \\
\texorpdfstring{Te\textsubscript{132}}{Te132} & 1.61 $\pm 0.37$ & 3.180 d \cite{Te132} \\
\texorpdfstring{I\textsubscript{132}}{I132} & 0.017 $\pm 0.11$  & 2.295 h \cite{Te132} \\
\texorpdfstring{Te\textsubscript{133}}{Te133} & 3.93 $\pm 0.15$ & 12.5 m \cite{iaeafissionyield} \\
\texorpdfstring{I\textsubscript{133}}{I133} & 0.153 $\pm 0.053$ & 20.87 h \cite{I133} \\
\texorpdfstring{Te\textsubscript{134}}{Te134} & 6.00 $\pm 0.47$ & 41.8 m \cite{iaeafissionyield} \\
\texorpdfstring{I\textsubscript{134}}{I134} & 0.900 $\pm 0.08$  & 52.5 m \cite{Sonzogni2004} \\
\texorpdfstring{Te\textsubscript{135}}{Te135} & 3.683 $\pm 0.56$ & 19.0 s \cite{iaeafissionyield} \\
\texorpdfstring{I\textsubscript{135}}{I135} & 2.550 $\pm 0.54$ & 6.58 h \cite{Singh2008} \\ \hline
\end{tabular}
\end{center}
\end{table}

>>>>

Nuclear fuel claddings have unique materials challenges owing to the highly active environment in which they operate and the creation of unstable isotopes. Corrosive species in the pin such as iodine, produced directly as a result of uranium fission are known to play a role in SCC \cite{Sidky1998, Fregonese1998, iodinezrmetal}. However, iodine nuclei produced from fission are unstable. Fission of uranium produces iodine precursors, mainly unstable isotopes of tellurium. Isotopes of iodine and tellurium are some of the most common fission products, with combined independent yields from thermal fission of U$_{235}$ of more than 25\%. In addition, xenon and caesium are also common fission products, as shown in Figure \ref{fig:fissionyield}, with fission product masses firmly within the heavy nuclide peak of uranium and plutonium fission product distribution curves.    \\ %\cite{kennett1956mass, iodine129fissionyield, imanishi1976independent, iodine132, amiel1975odd}

@@

\begin{table}
\caption{Independent fission product yields and half-lives for the major iodine isotopes and precursors in a thermal neutron reactor. Yields from the Joint Evaluated Fission and Fusion File (JEFF 3.3). All isotopes undergo single $\beta$- decay. Metastable states are included.}  \label{table:decaydata}
\begin{center}
\begin{tabular}{c c c}
\hline
Isotope & Independent Yield (\%) & Half-life \\
\hline
\texorpdfstring{I\textsubscript{131}}{I131} & 0.0029604
 & 8.023 d \cite{I131halflife} \\
\texorpdfstring{Te\textsubscript{132}}{Te132} & 1.5042 & 3.180 d \cite{Te132} \\
\texorpdfstring{I\textsubscript{132}}{I132} & 0.028399  & 2.295 h \cite{Te132} \\
\texorpdfstring{Te\textsubscript{133}}{Te133} & 3.9386 & 12.5 m \cite{khazov2011nuclear} \\
\texorpdfstring{I\textsubscript{133}}{I133} & 0.198194  & 20.87 h \cite{I133} \\
\texorpdfstring{Te\textsubscript{134}}{Te134} & 6.3001 & 41.8 m \cite{Sonzogni2004} \\
\texorpdfstring{I\textsubscript{134}}{I134} & 0.7673 & 52.5 m \cite{Sonzogni2004} \\
\texorpdfstring{Te\textsubscript{135}}{Te135} & 3.4777 & 19.0 s \cite{tellurium135halflife} \\
\texorpdfstring{I\textsubscript{135}}{I135} & 2.4635 & 6.58 h \cite{Singh2008} \\ 
\texorpdfstring{Te\textsubscript{136}}{Te136} & 1.6652 & 17.63  s \cite{Mccutchan2018NuclearA=136} \\
\texorpdfstring{I\textsubscript{136}}{I136} & 3.03823 & 83.4 s \cite{Mccutchan2018NuclearA=136} \\
\texorpdfstring{Te\textsubscript{137}}{Te137} & 0.48440 & 2.49 s \cite{browne2007nuclear} \\
\texorpdfstring{I\textsubscript{137}}{I137} & 2.7026 & 24.5 s \cite{browne2007nuclear} \\ 
\texorpdfstring{Te\textsubscript{138}}{Te138} & 0.11280 & 1.4 s \cite{chen2017nuclear} \\ 
\texorpdfstring{I\textsubscript{138}}{I138} & 1.2419 & 6.26 s \cite{chen2017nuclear} \\  \hline
\end{tabular}
\end{center}
\end{table}
